### 2015-07-23 usecase-ares.tex
Update ares table.

ARES comprises 47 packages, with complex dependency relationships. 
Figure~\ref{fig:ares} shows the DAG for the current production configuration 
of ARES. At the top is ARES itself.  ARES depends on 11 LLNL physics packages 
(red), 4 LLNL math/meshing libraries (gold), and 8 LLNL utility libraries 
(green). The utility libraries handle tasks including logging, I/O, and 
performance measurement. ARES also uses 23 external software packages, 
including MPI, BLAS, Python, and many other libraries.  Together, these 
packages ares written in a diverse set of languages including C, C++, 
Fortran, Python and tcl and uses MPI and OpenMP for parallelism.

@@

\begin{table}\centering
\begin{tabular}{|r|c|c|c|c|}
\hline
\multirow{2}{*}{} & \multicolumn{2}{|c|}{\bf Linux} & {\bf BG/Q}     & {\bf Cray XE6} \\\cline{2-5}
                  & {\it MVAPICH} & {\it OpenMPI}   & {\it BG/Q MPI} & {\it Cray MPI} \\\hline
{\bf GCC}         & {\tt C P L D} &                 &                &                \\\hline
{\bf Intel}       & {\tt C P L D} & {\tt C P L D}   &                &                \\\hline
{\bf PGI}         & {\tt C P L D} &                 &                & {\tt C P L D}  \\\hline
{\bf Clang}       & {\tt C P L D} &                 & {\tt C P L D}  &                \\\hline
{\bf XL}          &               &                 & {\tt C P L D}  &                \\\hline
\end{tabular}
\caption{
	Configurations of ARES built with Spack: \newline
	(C)urrent and
	(P)revious production, (L)ite, and (D)evelopment).
	\label{tab:ares-configs}
}
\end{table}

>>>>

ARES comprises 47 packages, with complex dependency relationships. 
Figure~\ref{fig:ares} shows the DAG for the current production configuration 
of ARES. At the top is ARES itself.  ARES depends on 11 LLNL physics packages 
(red), 4 LLNL math/meshing libraries (gold), and 8 LLNL utility libraries 
(green). The utility libraries handle tasks including logging, I/O, and 
performance measurement. ARES also uses 23 external software packages, 
including MPI, BLAS, Python, and many other libraries.  Together, these 
packages are written in a diverse set of languages including C, C++, 
Fortran, Python and tcl and uses MPI and OpenMP for parallelism.

@@

\newcommand{\hfmt}[1]{\textit{\scriptsize #1}}
\newcommand{\cfmt}[1]{\texttt{\scriptsize #1}}

\begin{table}\centering % mvapich2 for intel 15
\footnotesize
\begin{tabular}{|r|c|c|c|c|c|}
\hline
\multirow{2}{*}{} & \multicolumn{3}{|c|}{\hfmt{Linux}}                      & {\hfmt{BG/Q}}     & {\hfmt{Cray XE6}} \\\cline{2-6}
                  & {\hfmt{MVAPICH}} & {\hfmt{MVAPICH2}} & {\hfmt{OpenMPI}} & {\hfmt{BG/Q MPI}} & {\hfmt{Cray MPI}} \\\hline
{\hfmt{GCC}}      & {\cfmt{C P L D}} &                   &                  &                   &                   \\\hline
{\hfmt{Intel 14}} & {\cfmt{C P L D}} &                   &                  &                   &                   \\\hline
{\hfmt{Intel 15}} & {\cfmt{C P L D}} & {\cfmt{D}}        &                  &                   &                   \\\hline
{\hfmt{PGI}}      &                  & {\cfmt{D}}        & {\cfmt{C P L D}} &                   & {\cfmt{C L D}}    \\\hline
{\hfmt{Clang}}    & {\cfmt{C P L D}} &                   &                  & {\cfmt{C L D}}    &                   \\\hline
{\hfmt{XL}}       &                  &                   &                  & {\cfmt{C P L D}}  &                   \\\hline
\end{tabular}
\caption{
	Configurations of ARES built with Spack: \newline
	(C)urrent and
	(P)revious production, (L)ite, and (D)evelopment).
	\label{tab:ares-configs}
}
\end{table}
